Towards atomistic resolution structure of phosphatidylcholine glycerol backbone and choline headgroup at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}

### 2015-04-14 HGmodelMANUSCRIPT/HGmodel_ACStemplate.tex
add Hogberg et al. simulation file citations

\subsection{Simulated systems}
All simulations are ran with a standard setup for a planar lipid bilayer in zero tension and constant temperature
with periodic boundary conditions in all directions by using the GROMACS software package~\cite{hess08} 
(version numbers 4.5.X--4.6.X) or LAMMPS~\cite{plimpton95}.
The number of molecules, simulation temperatures and the length of simulations of all the simulated systems 
are listed in Tables~\ref{systems},~\ref{systemsDEHYD} and~\ref{systemsCHOL}. Full simulation
details are given in the Supplementary Information (SI) or in the original publications in case the
data is used previously therein. Additionally, the files related to the simulations and the resulting trajectories are publicly
available for almost all systems in the Zenodo collection \url{https://zenodo.org/collection/user-nmrlipids}. 
The references pointing to simulation details and files are also listed in Tables~\ref{systems},~\ref{systemsDEHYD} and~\ref{systemsCHOL}.

@@

H\"ogberg08 \cite{rabinovich14}  & POPC   &  128 & 3840  & 303 & 100 & 80  & - & [\citenum{rabinovich14}]  \\
H\"ogberg08 \cite{hogberg08}  & DMPC   &  98 & 3840  & 303 & 75 & 50 & - & [\citenum{hogberg08}] \\

@@

\subsection{Author Contributions}
\todo{Please write a text summarizing your contribution} \\
{\it Alexandru Botan} provided simulation results for charmm36-UA\\
{\it Fernando Favela} prepared, performed and analyzed simulations
with popc and cholesterol for the CHARMM36 All-Atom FF. \\
{\it Patrick F. J. Fuchs} Ran and analyzed the Poger simulations. Provided scientific information which significantly advanced the project (signs and forking of order parameters). \\
{\it Matti Javanainen} prepared and performed simulations with multiple lipid models and analyzed the results. Supervised the work of JT.\\
{\it Matej Kanduc} provided simulation results for the Berger DLPC model \\
{\it Waldemar Kulig} prepared the MD simulations with cholesterol for the MacRog FF \\
{\it Antti Lamberg}  \\
{\it Claire Loison} provided simulation results for charmm36-UA \\
{\it Markus S. Miettinen}  \\
{\it Luca Monticelli}  \\
{\it Jukka M{\"a}{\"a}tt{\"a}}  prepared and performed simulations with Berger and Slipids models and analyzed the results.\\
{\it O. H. Samuli Ollila} Designed and managed the work. Ran and analyzed several simulations. Wrote the manuscript.  \\
{\it Marius Retegan} Prepared and validated the GROMACS compatible parameter files for GAFFlipid and Lipid14 force fields.\\
{\it Tomasz Rog}  \\
{\it Hubert Santuz} prepared and performed the cholesterol simulations with CHARMM36 and analyzed the results. \\
{\it Joona Tynkkynen} prepared and performed the dehydration simulations with the MacRog FF.\\

>>>>

\subsection{Simulated systems}
All simulations are ran with a standard setup for a planar lipid bilayer in zero tension and constant temperature
with periodic boundary conditions in all directions by using the GROMACS software package~\cite{hess08} 
(version numbers 4.5.X--4.6.X), LAMMPS~\cite{plimpton95} or MDynaMix~\cite{Lyubartsev00}.
The number of molecules, simulation temperatures and the length of simulations of all the simulated systems 
are listed in Tables~\ref{systems},~\ref{systemsDEHYD} and~\ref{systemsCHOL}. Full simulation
details are given in the Supplementary Information (SI) or in the original publications in case the
data is used previously therein. Additionally, the files related to the simulations and the resulting trajectories are publicly
available for almost all systems in the Zenodo collection \url{https://zenodo.org/collection/user-nmrlipids}. 
The references pointing to simulation details and files are also listed in Tables~\ref{systems},~\ref{systemsDEHYD} and~\ref{systemsCHOL}.

@@

H\"ogberg08 \cite{rabinovich14}  & POPC   &  128 & 3840  & 303 & 100 & 80  &  [\citenum{hogbergPOPCfiles}]$^*$ & [\citenum{rabinovich14}]  \\
H\"ogberg08 \cite{hogberg08}  & DMPC   &  98 & 3840  & 303 & 75 & 50 &  [\citenum{hogbergDMPCfiles}]$^*$ & [\citenum{hogberg08}] \\

@@

\subsection{Author Contributions}
\todo{Please write a text summarizing your contribution} \\
{\it Alexandru Botan} provided simulation results for charmm36-UA\\
{\it Fernando Favela} prepared, performed and analyzed simulations
with popc and cholesterol for the CHARMM36 All-Atom FF. \\
{\it Patrick F. J. Fuchs} Ran and analyzed the Poger simulations. Provided scientific information which significantly advanced the project (signs and forking of order parameters). \\
{\it Matti Javanainen} prepared and performed simulations with multiple lipid models and analyzed the results. Supervised the work of JT.\\
{\it Matej Kanduc} provided simulation results for the Berger DLPC model \\
{\it Waldemar Kulig} prepared the MD simulations with cholesterol for the MacRog FF \\
{\it Antti Lamberg}  \\
{\it Claire Loison} provided simulation results for charmm36-UA \\
{\it Markus S. Miettinen}  \\
{\it Luca Monticelli}  \\
{\it Jukka M{\"a}{\"a}tt{\"a}}  prepared and performed simulations with Berger and Slipids models and analyzed the results.\\
{\it O. H. Samuli Ollila} Designed and managed the work. Ran and analyzed several simulations. Wrote the manuscript.  \\
{\it Marius Retegan} Prepared and validated the GROMACS compatible parameter files for GAFFlipid and Lipid14 force fields.\\
{\it Tomasz Rog} Provided the topologies for the MacRog model and also the full hydration simulation data with this model. \\
{\it Hubert Santuz} prepared and performed the cholesterol simulations with CHARMM36 and analyzed the results. \\
{\it Joona Tynkkynen} prepared and performed the dehydration simulations with the MacRog FF.\\
